---
title: "An analysis of English Premier League Data from 1992-2022"
output: word_document
date: "2024-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require("ggplot2")){install.packages("ggplot2")}
if(!require("flextable")){install.packages("flextable")}
if(!require("psych")){install.packages("psych")}
if(!require("tableone")){install.packages("tableone")}

library(ggplot2)
library(flextable)
library(psych)
library(tableone)
```

# An Introduction to the Data

Dataset is thanks to Evan Gower on Kaggle, and can be found at: https://www.kaggle.com/datasets/evangower/premier-league-matches-19922022

Each entry represents an English Premier League match with the following information:

+ **Season_End_Year** - The Year that the Season ends in.
+ **Wk** - The Game Week.
+ **Date** - Date the Game took place on.
+ **Home** - The Home Team.
+ **HomeGoals** - Amount of Goals scored by the Home Team.
+ **AwayGoals** - Amount of Goals scored by the Away Team.
+ **Away** - The Away Team.
+ **FTR** - Full Time Result. (H - Home Win, D - Draw, A - Away Win)

```{r echo=FALSE}
results <- read.csv("data/premier-league-matches.csv")
head(results)
```
# brief Dataset Exploration
```{r echo = FALSE}
home_goal_counts <- as.data.frame(table(results$HomeGoals))
colnames(home_goal_counts) <- c("Goals", "Frequency")

ggplot(home_goal_counts, aes(x=Goals, y=Frequency)) + geom_bar(stat="identity") + labs(title = "Frequency of Goals Scored by Home side in EPL", x = "Number of Goals", y = "Frequency") + theme_minimal()

```

