---
title: "An analysis of English Premier League Data from 1992-2022"
output: word_document
date: "2024-10-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# An Introduction to the Data

Dataset is thanks to Evan Gower on Kaggle, and can be found at: https://www.kaggle.com/datasets/evangower/premier-league-matches-19922022

Each entry represents an English Premier League match with the following information:

+ **Season_End_Year** - The Year that the Season ends in.
+ **Wk** - The Game Week.
+ **Date** - Date the Game took place on.
+ **Home** - The Home Team.
+ **HomeGoals** - Amount of Goals scored by the Home Team.
+ **AwayGoals** - Amount of Goals scored by the Away Team.
+ **Away** - The Away Team.
+ **FTR** - Full Time Result. (H - Home Win, D - Draw, A - Away Win)

```{r echo=FALSE}
results <- read.csv("data/premier-league-matches.csv")
head(results)
```
# How many unique teams have played in the Premier League?
A brief exploration shows that 50 unique teams have played in the Premier League.
```{r echo=FALSE}
all_epl_sides <- sort(unique(c(results$Home, results$Away)))
length(all_epl_sides)
all_epl_sides
```
## Which Teams have played the most Games?

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
